Multi-resolution Neural Field Estimation

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
more edits with parham

	\mathbf y_t = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 

@@

\section{Results}
To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated. The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$). The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. \dean{The number of states $n_x = ??$.} The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations. \dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.} The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{freestone2011}. Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field. 
% \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

\parham{Field reconstruction obtained using the state estimates of the EM algorithm at different levels of approximations separately using same observation set. (\figurename{\ref{fig:FieldEstimates}})}. The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72. The confirms good state estimation performance, where the estimated field is in good accordance with the true field. The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The small error in the estimate is attributed to the MRA of the system used to form the estimator.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Field.pdf}
		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE = 2.10. (b) $j=1$, $n_x=33$, RMSE = 1.42. (c) $j=2$, $n_x=65$, RMSE = 0.80. (d) $j=3$, $n_x=131$, RMSE = 0.72. (e) $j=4$, $n_x=263$, RMSE=0.72.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Kernel.pdf}
		\caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
	\label{fig:KernelEstimate}
\end{figure}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...

>>>>

	y_t(\mathbf{r}_n) = \int_{\Omega} { m\left(\mathbf{r}_{n}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t, 

@@

\section{Results}
To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated. The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$). The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations. The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}. Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = ??$ states. \dean{With this number of observations, the estimation problem was well-posed, since the wavelet are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}  
% \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

\parham{Field reconstruction obtained using the state estimates of the EM algorithm at different levels of approximations separately using same observation set. (\figurename{\ref{fig:FieldEstimates}})}. The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72. Figure 3 confirms good state estimation performance, where the estimated field is in good accordance with the true field.

The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The small error in the estimate is attributed to the MRA of the system used to form the estimator.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Field.pdf}
		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE = 2.10. (b) $j=1$, $n_x=33$, RMSE = 1.42. (c) $j=2$, $n_x=65$, RMSE = 0.80. (d) $j=3$, $n_x=131$, RMSE = 0.72. (e) $j=4$, $n_x=263$, RMSE=0.72.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Kernel.pdf}
		\caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
	\label{fig:KernelEstimate}
\end{figure}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...
